Reinforcement Learning Produces Dominant Strategies for the Iterated Prisoner's Dilemma

### 2017-07-04 main.tex
Add plots and tables for 15k reps.
All automatically generated from src/main.ipynb.

Includes more detailed summary tables.

Also removing unneeded plots. Everything is in assets.

We conducted a tournament with all strategies in the Axelrod library. The top
11 performing strategies by mean payoff are all strategies trained to maximize
total payoff against a subset of the strategies (Table \ref{tbl:standard_score}).
The next strategy is
Desired Belief Strategy (DBS) which actively analyzes the opponent and responds
accordingly. The next two strategies are Winner12, based on a lookup table,
Omega TFT, and Fool Me Once, a grudging strategy that defects indefinitely on
the second defection. All strategies in the tournament follow a simple set of
rules in accordance with earlier tournaments:
\begin{itemize}
  \item Players carry no acquired state between matches
  \item Players cannot observe the outcome of other matches
  \item Players cannot identify their opponent by any label or identifier
  \item Players cannot manipulate or inspect their opponents in any way
\end{itemize}

Pairwise payoff results are given as a heatmap (Figure ) which
shows that many strategies achieve mutual cooperation with each other and
that the top performing strategies never defect first but are able to exploit
weaker strategies that attempt to defect.

The strategies that win the most matches are Defector, Aggravater, followed by
handshaking and zero determinant strategies. This includes two handshaking
strategies that were the result of training to maximize Moran process fixation.
No strategies were trained specifically to win matches. None of the top scoring
strategies appear in the top 20 list of strategies ranked by match wins.

% Table of best strategies
\begin{table}[!hbtp]
    \centering
        \input{./tex/standard_scores.tex}
        \caption{Standard Tournament: Top Ranking Strategies by Median Score in 15,000 Tournaments}
        \label{tbl:standard_score}
\end{table}

\begin{landscape}
    \begin{figure}[!hbtp]
        \includegraphics[width=\paperwidth]{plots/Standard_boxplot.pdf}
        \caption{Ranking by Median Payoff for the Standard Tournament}
    \end{figure}
\end{landscape}

\begin{landscape}
    \begin{figure}[!hbtp]
        \includegraphics[width=\paperwidth]{plots/Standard_winplot.pdf}
        \caption{Ranking by Total wins for the Standard Tournament}
    \end{figure}
\end{landscape}

\begin{figure}[!hbtp]
    \includegraphics[width=\paperwidth]{plots/Standard_payoff.pdf}
    \caption{Pairwise Match results for the Standard Tournament}
\end{figure}

>>>>

We conducted a tournament with all strategies in the Axelrod library, including
some parametrized strategies. These are listed in
Appendix~\ref{app:list_of_players}.
% TODO Add list of players
The top
11 performing strategies by median payoff are all strategies trained to maximize
% TODO Potentially modify this as more repetitions are analysed.
total payoff against a subset of the strategies (Table~\ref{tbl:standard_score}).
The next strategy is
Desired Belief Strategy (DBS)
% TODO Add reference for DBS
which actively analyzes the opponent and responds
accordingly. The next two strategies are Winner12, based on a lookup table,
Fool Me Once, a grudging strategy that defects indefinitely on
the second defection and Omega Tit For Tat.
% TODO Add a reference for Omega TfT
All strategies in the tournament follow a simple set of
rules in accordance with earlier tournaments:

\begin{itemize}
  \item Players are unaware of the number of turns in a match
  \item Players carry no acquired state between matches
  \item Players cannot observe the outcome of other matches
  \item Players cannot identify their opponent by any label or identifier
  \item Players cannot manipulate or inspect their opponents in any way
\end{itemize}

% Table of best strategies
\begin{table}[!hbtp]
    \centering
        \input{./assets/standard_top_15_scores_summary.tex}
        \caption{Standard Tournament: Top Ranking Strategies by median score
        (50th percentile) in 15,000 Tournaments}
        % TODO Update caption as more repetitions are carried out
        % TODO Potentially remove count from table (including it for now so as
        % to avoid confusion.
        \label{tbl:standard_score}
\end{table}

Violin plots showing the distribution of the scores of each strategy (again
ranked by median score) are shown in Figure~\ref{fig:standard_boxplot}.

\begin{landscape}
    \begin{figure}[!hbtp]
        \includegraphics[width=\paperwidth]{./assets/standard_scores_boxplots.pdf}
        \caption{Ranking by median score for the Standard Tournament}
        \label{fig:standard_boxplot}
    \end{figure}
\end{landscape}

Pairwise payoff results are given as a heatmap (Figure~\ref{fig:standard_heatmap})
which shows that many strategies achieve mutual cooperation with each other and
that the top performing strategies never defect first but are able to exploit
weaker strategies that attempt to defect.

\begin{figure}[!hbtp]
    \includegraphics[width=\textwidth]{./assets/standard_scores_heatmap.pdf}
    \caption{Pairwise Match results for the Standard Tournament}
    \label{fig:standard_heatmap}
\end{figure}

The strategies that win the most matches are Defector, Aggravater, followed by
handshaking and zero determinant strategies. This includes two handshaking
strategies that were the result of training to maximize Moran process fixation.
No strategies were trained specifically to win matches.
None of the top scoring
strategies appear in the top 20 list of strategies ranked by match wins.
This can be seen in Figure~\ref{fig:standard_winplot} where the distribution of
the number of wins of each strategy is shown.

\begin{landscape}
    \begin{figure}[!hbtp]
        \centering
        \includegraphics[width=\textwidth]{./assets/standard_wins_boxplots.pdf}
        \caption{Ranking by Total wins for the Standard Tournament}
        \label{fig:standard_winplot}
    \end{figure}
\end{landscape}

The number of wins of the top strategies of Table~\ref{tbl:standard_wins} are
shown in Table~\ref{tbl:standard_wins}. It is evident that although these
strategies score highly they do not win many matches: the strategy with the most
number of wins is the Evolved FSM 16 strategy that at most won 60
(\(60/175\approx34\%\)) matches in a given tournament.
% TODO Update this when more data comes in.

\begin{table}[!hbtp]
    \centering
        \input{./assets/standard_top_15_wins_summary.tex}
        \caption{Standard Tournament: Number of wins of Top Ranking Strategies
        by median score (50th percentile) in 15,000 Tournaments}
        % TODO Update caption as more repetitions are carried out
        % TODO Potentially remove count from table (including it for now so as
        % to avoid confusion.
        \label{tbl:standard_wins}
\end{table}

Finally, Table~\ref{tbl:standard_ranks} and
Figure~\ref{fig:standard_ranks_boxplot} show the ranks (based on median score)
of each strategy over the repeated tournaments. Whilst there is some
stochasticity, the top three strategies almost always rank in the top three. For
example, the worst that the Evolved Lookerup 2 2 2 ranks in a given tournament
is 7th.

\begin{table}[!hbtp]
    \centering
        \input{./assets/standard_top_15_ranks_summary.tex}
        \caption{Standard Tournament: Ranks of Top Ranking Strategies
        by median score (50th percentile) in 15,000 Tournaments}
        % TODO Update caption as more repetitions are carried out
        % TODO Potentially remove count from table (including it for now so as
        % to avoid confusion.
        \label{tbl:standard_ranks}
\end{table}

\begin{landscape}
    \begin{figure}[!hbtp]
        \centering
        \includegraphics[width=\textwidth]{./assets/standard_ranks_boxplots.pdf}
        \caption{Rankings over each repeated tournament}
        \label{fig:standard_ranks_boxplot}
    \end{figure}
\end{landscape}

Using the method of fingerprinting described in \cite{ashlock2008fingerprinting}
% TODO This is actually a numerical approximation of the fingerprinting
% described in ashlock's paper. There they consider a fingerprint to be an
% analytic function.
\cite{ashlock2009fingerprint}, we can compare
strategies. For the top performing noisy strategies there is a striking similarity
in the fingerprints.
